Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex
Experiments

\section{Experiments}
\label{sec:experiments}
%
We present a series of experiments designed to demonstrate the versatility and efficacy of \our. We seek to find answers to the following questions: 
\textbf{Predictions:}~Does our method's ability to consider the full data set offer benefits over subset function-space methods? (\cref{sec:uci}) How do predictions with our sparse function-space approximation compare to weight-space approximations? 
\textbf{Function-space updates:} How fast are our function-space updates relative to retraining from scratch? Do they improve predictive performance? 
\textbf{Representation:} Can a sparse function-space representation help retain knowledge from previous tasks in CL? (\cref{sec:cl-exp})
\textbf{Uncertainty:} Can our uncertainty estimates help exploration in RL? (\cref{sec:rl-exp})

\paragraph{Implementation} We implement all methods in PyTorch~\cite{paszke2019pytorch} and leverange the XXXX libraries.. \todo{add brief details}. Experiments were run on clusters

\paragraph{Toy examples} For illustrative purposes, we smoke-test our approach on a 1D regression problem (\cref{fig:teaser}) and on the 2D Banana classification task (\cref{fig:banana}). In \cref{fig:teaser}, we train an MLP neural network with two hidden layers (64 hidden units each, tanh activation). The middle panel shows the \our result on a sparse set of data examples, while the rightmost panel demonstrates fast dual conditioning on new data (from \cref{sec:sequential}). In \cref{fig:banana}, we use an MLP with two hidden layers (64 units, sigmoid) and compare to the HMC result obtained by hamiltorch \cite{cobb2020scaling} that shows capture similar behaviour as HMC.

>>>>

\section{Experiments}
\label{sec:experiments}
%
We present a series of experiments specifically designed to showcase the robustness and effectiveness of \our. The experiments are aimed at answering the following key questions:
\textbf{Predictions:}~Does our method's ability to consider the full data set offer benefits over subset function-space methods? (\cref{sec:uci}) How do predictions with our sparse function-space approximation compare to weight-space approximations? 
\textbf{Function-space updates:} How fast are our function-space updates relative to retraining from scratch? Do they improve predictive performance? 
\textbf{Representation:} Can a sparse function-space representation help retain knowledge from previous tasks in CL? (\cref{sec:cl-exp})
\textbf{Uncertainty:} Can our uncertainty estimates help exploration in RL? (\cref{sec:rl-exp}) We implement all methods in PyTorch~\cite{paszke2019pytorch} and run the benchmarks using a GPU cluster. We provide full experiment details in \cref{app:experiments}.

\paragraph{Toy examples} For illustrative purposes, we show our approach on a 1D regression problem (\cref{fig:teaser}) and on the 2D {\sc Banana} classification task (\cref{fig:banana}). In \cref{fig:teaser}, we train an MLP neural network with two hidden layers (64 hidden units each, tanh activation) and pass it through \our. The middle panel shows the \our result on a sparse set of data examples, while the rightmost panel demonstrates fast dual conditioning on new data (from \cref{sec:sequential}). In \cref{fig:banana}, we use an MLP with two hidden layers (64 units, sigmoid) and compare to a HMC sampling result obtained by hamiltorch~\cite{cobb2020scaling}. The HMC result is more expressive, but the results are still similar in terms of quantifying the uncertainty in low-data regions.
